### 2021-07-14 src/paper/data/course_of_disease.tex
More polishing.

This section discusses the parameters governing the course of disease, their sources and
how we arrived at the distributions used in the paper.\footnote{Additional information
can be found in the
\href{https://sid-dev.readthedocs.io/en/latest/reference_guides/epi_params.html}{online
documentation}.} See Figure~\ref{fig:model_disease_progression} for a summary of our
disease progression model.

>>>>

This section discusses the parameters governing the course of disease, their sources and
how we arrived at the distributions used in the paper.
See Figure~\ref{fig:model_disease_progression} for a summary of our
disease progression model.

### 2021-07-14 src/paper/results/fit.tex
More polishing.

This section compares simulated data from our model with empirical data from Germany. We
look at observed infections (overall as well as by age group and federal state), the
effective replication number,  the spread of the B.1.1.7 mutation,
vaccinations.

@@

  \floatfoot{\noindent \textit{Note:} Both figures show averages and single runs. The
  average is the thick line. Single runs are shown as lighter and thinner lines. We
  averaged and show 30 simulation runs. The left figure shows the daily incidence rate
  per million for the simulated reported infection rates. The mean infection rate is the
  thick blue line. Single simulation runs are plotted in lighter and thinner lines. The
  official case numbers as reported by the RKI are plotted in black. The fit is overall
  very good. The higher the mean incidence and the stronger the growth the more variance
  there is between simulation runs. The right figure shows the effective replication
  number ($R_t$) as reported by the RKI and as calculated in our model. The $R_t$ gives
  the average number of new infections caused by one infected individual. The $R_t$ in
  our model broadly follows the $R_t$ reported by the RKI. Two differences stand out.
  Firstly, the RKI's $R_t$ drops faster in November. This is likely due to a decline in
  the estimated overall share of detected cases ($\psi_t$) when the second wave hit
  Germany. The second difference is from mid February to mid March where the RKI's
  reported $R_t$ increased more rapidly than that in our model. Here the opposite effect
  can be expected. During this time rapid tests increased strongly leading to more cases
  being detected. In the short term this leads an $R_t$ estimation that is based on
  detected cases to overestimate the replication number.}
\end{figure}

@@

% observed infections by age group
Zooming into the different age groups in Figure~\ref{fig:age_group_fit}, we can see that
our model is also able to reproduce the infection rates on this level. The only major
deviation from this pattern is that our model predicts too few infections for the 80 to
100 year olds. This was to be expected because our synthetic population does not include
inhabitants of nursing homes. Outbreaks in nursing homes led to a large number of
infections among the oldest during the second wave of the pandemic in Germany. Moreover,
the model predicts too few observed infections for the 15 to 34 years old at the end of
2020 and the 5 to 14 years old in April and May 2021. The former is likely due to the
fact that this age group has a very active social life which is not fully captured by our
contact networks. The latter probably comes from too optimistic\comment[id=K]{cautious or
slow? I think optimistic might be ambiguous here.} assumptions on school reopenings.

\begin{figure}[ht]  % observed infections by age group
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/incidences_by_group/age_group_rki/full_combined_baseline_new_known_case}
  \caption{Simulated and Empirical Infections by Age Group}
  \floatfoot{\noindent \textit{Note:} The figure shows the number of reported versus
  simulated cases per one million people per day for different age groups. The age group
  of individuals above 80 needs to be interpreted with caution because our synthetic
  population only includes private households, i.e. nursing homes are not represented in
  our model. They accounted for many cases and deaths in the winter of 2020 and many 80
  to 100 year olds live in these facilities. We average over 30
  simulation runs.}
  \label{fig:age_group_fit}
\end{figure}

@@

\begin{figure}[ht]   % observed infections by federal state
  \centering
  \includegraphics[height=0.95\textheight]{figures/results/figures/incidences_by_group/state/full_combined_baseline_new_known_case}
  \caption{Simulated and Empirical Infections by Federal State}
  \floatfoot{\noindent \textit{Note:} The figure shows the number of reported versus
  simulated cases per one million people per day for different federal states. We
  averaged over 30 simulation runs.}
  \label{fig:state_fit}
\end{figure}

@@

  \begin{subfigure}[b]{0.425\textwidth}   % Share B.1.1.7
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_share_b117_with_single_runs}
    \caption{Share of B.1.1.7 in the Model and as Reported by the RKI}
    \label{fig:fit_share_b117}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.425\textwidth}    % Vaccinations
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_ever_vaccinated}
    \caption{Share of Vaccinated Individuals in the Model and the German Population}
    \label{fig:fit_vaccinations}
  \end{subfigure}
  \caption{Model Fit of the Share of B.1.1.7 and Vaccinations}
  \floatfoot{\noindent \textit{Note:} The left figure shows the share of B.1.1.7 as
  reported by the RKI and as calculated in our model. We only introduce a few cases over
  the course of January. From then B.1.1.7 takes over endogenously through its increased
  infectiousness ($\sigma_{B.1.1.7}$). We model no other features of B.1.1.7. We
  introduce at most 0.986 cases per 100,000 inhabitants. The right figure shows the rate
  of individuals that are vaccinated in our synthetic population versus in the general
  German population. Note that we excluded the vaccinations that were given to nursing
  homes (approx. one percent of the German population). Overall, our model covers a time
  frame that goes from zero vaccinated individuals to a state where over 40\% of the
  population are vaccinated. Our vaccinations work imperfectly but we do not model
  different different vaccines nor do we distinguish between first and second shot.}
\end{figure}

@@

% rapid test demand
The most difficult moment to match in our model is the rapid test demand. This is because
we have five different channels through which individuals demand rapid tests and many of
the demand curves are at least partially calibrated through survey data. It is therefore
very reassuring that we fit the share of individuals that do weekly rapid tests almost
perfectly. For the share of individuals that have ever done a rapid test our model is
conservative. There are two reasons for this: Firstly, we do not model people who have
made rapid tests out of curiosity once they became available. Secondly, in the model, the
decision to take a rapid test is based on a time invariant individual specific compliance
factor without any additional random components. While this captures important features
of rapid test demand it abstracts from people who turn down rapid tests most of the time
but accept them sometimes. Fortunately, Section~\ref{subsec:model_validation} shows that
our main results are robust to changes in the exact shares of individuals demanding rapid
tests.

\begin{figure}[ht]     % rapid test demand
    \centering
    \caption{Share of Individuals With Rapid Tests}
    \label{fig:share_ever_rapid_test2}
    \begin{subfigure}{.425\textwidth}
        \includegraphics[width=0.9 \textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_share_ever_rapid_test}
        \caption{Share of the Population That Has Ever Done a Rapid Test}
    \end{subfigure}%
    \hfill
    \begin{subfigure}{.425\textwidth}
        \includegraphics[width=0.9 \textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_share_rapid_test_in_last_week}
        \caption{Share of the Population That Did a Rapid Test in the Last Week}
    \end{subfigure}
    \label{fig:share_rapid_test_last_week2}
    \floatfoot{\noindent \textit{Note:} The figure compares the share of individuals who
        have ever done a rapid test or done a rapid test within the last week in our
        simulations to the shares reported in \citet{Betsch2021b}. The left panel
        compares the share of individuals who have ever done a rapid test. The right
        panel compares the share of individuals who have done a rapid test within the
        last seven days in our simulation compared to the share reporting to have done at
        least weekly rapid tests in the last four weeks in the COSMO survey. Overall our
        calibration of rapid tests are slightly conservative. The overall share is below
        that in the study. We fit the share of weekly tests quite exactly. % However, the
        % study only covers adults while our share also includes children who are tested
        % very regularly when attending school.
      }
\end{figure}

>>>>

This section compares simulated data from our model with empirical data from Germany. We
look at observed infections (overall as well as by age group and federal state), the
effective replication number,  the spread of B.1.1.7 and vaccinations.

@@

  \floatfoot{\noindent \textit{Note:} Both figures show averages and single runs. The
  average is the thick line. Single runs are shown as lighter and thinner lines. We
  averaged and show 30 simulation runs. The left figure shows the daily incidence rate
  per million for the simulated reported infection rates. The
  official case numbers as reported by the RKI are plotted in black. The fit is overall
  very good. The right figure shows the effective replication
  number ($R_t$) as reported by the RKI and as calculated in our model. The $R_t$ gives
  the average number of new infections caused by one infected individual. The $R_t$ in
  our model broadly follows the $R_t$ reported by the RKI. Two differences stand out.
  Firstly, the RKI's $R_t$ drops faster in November. This is likely due to a decline in
  the estimated overall share of detected cases ($\psi_t$) when the second wave hit
  Germany. The second difference is from mid February to mid March where the RKI's
  reported $R_t$ increased more rapidly than that in our model. Here the opposite effect
  can be expected. During this time rapid tests increased strongly leading to more cases
  being detected. In the short term this leads an $R_t$ estimation that is based on
  detected cases to overestimate the replication number.
  For legibility reasons, all lines are rolling 7-day averages.}
\end{figure}

@@

% observed infections by age group
Zooming into the different age groups in Figure~\ref{fig:age_group_fit}, we can see that
our model is also able to reproduce the infection rates on this level. The only major
deviation from this pattern is that our model predicts too few infections for the 80 to
100 year olds. This was to be expected because our synthetic population does not include
inhabitants of nursing homes. Outbreaks in nursing homes led to a large number of
infections among the oldest during the second wave of the pandemic in Germany. Moreover,
the model predicts too few observed infections for the 15 to 34 years old at the end of
2020 and the 5 to 14 years old in April and May 2021. The former is likely due to the
fact that this age group has a very active social life which is not fully captured by our
contact networks. The latter probably comes from a too conservative model of school
reopenings.

\begin{figure}[ht]  % observed infections by age group
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/incidences_by_group/age_group_rki/full_combined_baseline_new_known_case}
  \caption{Simulated and Empirical Infections by Age Group}
  \floatfoot{\noindent \textit{Note:} The figure shows the number of reported versus
  simulated cases per one million people per day for different age groups. The age group
  of individuals above 80 needs to be interpreted with caution because our synthetic
  population only includes private households, i.e. nursing homes are not represented in
  our model. They accounted for many cases and deaths in the winter of 2020 and many 80
  to 100 year olds live in these facilities. We average over 30
  simulation runs. For legibility reasons, all lines are rolling 7-day averages.}
  \label{fig:age_group_fit}
\end{figure}

@@

\begin{figure}[ht]   % observed infections by federal state
  \centering
  \includegraphics[height=0.95\textheight]{figures/results/figures/incidences_by_group/state/full_combined_baseline_new_known_case}
  \caption{Simulated and Empirical Infections by Federal State}
  \floatfoot{\noindent \textit{Note:} The figure shows the number of reported versus
  simulated cases per one million people per day for different federal states. We
  averaged over 30 simulation runs. For legibility reasons, all lines are rolling 7-day averages.}
  \label{fig:state_fit}
\end{figure}

@@

  \begin{subfigure}[b]{0.425\textwidth}   % Share B.1.1.7
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_share_b117_with_single_runs}
    \caption{Share of B.1.1.7 in the Model and as Reported by the RKI}
    \label{fig:fit_share_b117}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.425\textwidth}    % Vaccinations
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_ever_vaccinated}
    \caption{Share of Vaccinated Individuals in the Model and the German Population}
    \label{fig:fit_vaccinations}
  \end{subfigure}
  \caption{Model Fit of the Share of B.1.1.7 and Vaccinations}
  \floatfoot{\noindent \textit{Note:} The left figure shows the share of B.1.1.7 as
  reported by the RKI and as calculated in our model. We only introduce a few cases over
  the course of January. From then B.1.1.7 takes over endogenously through its increased
  infectiousness ($\sigma_{B.1.1.7}$). The right figure shows the rate
  of individuals that are vaccinated in our synthetic population versus in the general
  German population. For legibility reasons, all lines are rolling 7-day averages.}
\end{figure}

@@

% rapid test demand
The most difficult moment to match in our model is the rapid test demand. This is because
we have five different channels through which individuals demand rapid tests and many of
the demand curves are at least partially calibrated through survey data. It is therefore
very reassuring that we fit the share of individuals that do weekly rapid tests almost
perfectly. For the share of individuals that have ever done a rapid test our model is
conservative. There are two reasons for this: Firstly, we do not model people who have
done rapid tests out of curiosity once they became available. Secondly, in the model, the
decision to take a rapid test is based on a time invariant individual specific compliance
factor without any additional random components. While this captures important features
of rapid test demand it abstracts from people who turn down rapid tests most of the time
but accept them sometimes. Fortunately, Section~\ref{subsec:model_validation} shows that
our main results are robust to changes in the exact shares of individuals demanding rapid
tests.

\begin{figure}[ht]     % rapid test demand
    \centering
    \caption{Share of Individuals With Rapid Tests}
    \label{fig:share_ever_rapid_test2}
    \begin{subfigure}{.425\textwidth}
        \includegraphics[width=0.9 \textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_share_ever_rapid_test}
        \caption{Share of the Population That Has Ever Done a Rapid Test}
    \end{subfigure}%
    \hfill
    \begin{subfigure}{.425\textwidth}
        \includegraphics[width=0.9 \textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_share_rapid_test_in_last_week}
        \caption{Share of the Population That Did a Rapid Test in the Last Week}
    \end{subfigure}
    \label{fig:share_rapid_test_last_week2}
    \floatfoot{\noindent \textit{Note:} Both panels compare empirical and simulated
        rapid test demands. The empirical data comes from \citet{Betsch2021b}.
        The left panel compares the share of individuals who have ever done a rapid test.
        The right
        panel compares the share of individuals who have done a rapid test within the
        last seven days in our simulation compared to the share reporting to have done at
        least weekly rapid tests in the last four weeks in the COSMO survey. Overall our
        calibration of rapid tests are slightly conservative. The overall share is below
        that in the study. We fit the share of weekly tests quite exactly.
        For legibility reasons, all simulated lines are rolling 7-day averages. % However, the
        % study only covers adults while our share also includes children who are tested
        % very regularly when attending school.
      }
\end{figure}
